---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# hpmicrosimr

<!-- badges: start -->
<!-- badges: end -->

*hpmicrosimr* is an agent-based model simulation framework describing home energy efficiency and heating technology system upgrades by 901 owner-occupier households. The model is initialised in, say, 2015 and can run to 2050.

This is an early development version of *hpmicrosimr*. The main functionality is the household financial return (bill savings). There is also an initialiser. The household investment decision involves a possible BER upgrade from BER_old -> BER_new and a possible technology shift from tech_old -> tech_new. *hpmicrosimr* calculates the full financial return tensor, and determines the optimum system, including the effect of grants applicable.A separate package *hpmicrocalibrater* is used to generate the model weights and thresholds and are provided in a dataset *agents_init* attached to *hpmicrosimr*. 


## Installation

The latest development version of *hpmicrosimr* can be installed as follows:

``` r
remotes::install_github("https://github.com/Phalacrocorax-gaimardi/hpmicrosimr")
```

## Example: Financial Return Tensor

Householders face a complex decision when considering home energy upgrades. For example, a detached house in Munster with 100m2 floor area is heated using an oil boiler in 2026. The house was built in 2003 and has a C2 BER score. The current version of *hpmicrosimr* ignores any secondary and tertiary heat sources that may be present or might be adopted by a household. With this assumption, we would like to know the financially optimal upgrade path. If the financial return is sufficient, this can overcome behavioural correction factors such as risk aversion, hassle, present bias etc.

First load in the technical and cost scenario parameters for 2026 *params*. A set of technology specific cost parameters are contained in *tech_parms* and are assumed to be fixed (apart from skilled labour cost). The default cost matrix for energy efficiency improvements is based on a marginal cost model $k_0 BER^{-\alpha}$. This captures the steep increase in that upgrade costs required to reach the lowest heat loss ratings A1, A2 etc.

```{r example}
library(hpmicrosimr)
params <- scenario_params(sD,2026)
tech_params <- tech_params_fun()
optimise_upgrade(ber_old=180,tech_old = "oil",house_type="detached",2003,region="Munster",floor_area=100,params)
```

The optimum upgrade in this case is to a B1 with a switch to a Heat Pump. However, replacing their oil boiler is a close second. Note that this calculation assumes no change in the heating comfort level demanded by households.

Familiarity with three high-level functions needed to run *hpmicrosimr*: the initialiser *initial_agents()*, the updater *update_agents()* and *run_abm()*. 


## Example: initialiser

The function *initialise_agents()* generates the initial state of the population of agents at a specific time. It based on 2024 survey data, projected backwards to, say, 2015. 

This function does quite a bit of work behind the scenes.It imputes missing values of BER, construction year and household income, for example. It also imputes the floor area of the property. If the initialisation time of the ABM is set to 2015, then only houses constructed before 2015 are included. If the installation year of the current heating system stated in the survey is later then 2015 then an installation date before 2015 is inferred for the earlier system. It is assumed that the heating technology used by the household in 2015 is the same as the technology used in 2024. The only exception is for heat pumps where it is assumed that heat pumps adopted after 2015 replaced an earlier gas or oil system. *initialise_agents()* also does a number of other recodings of the survey variables descroved in *hp_questions* and *hp_qanda*.

The initial state contains all data needed to evaluate the annual bill savings for each agent for all possible technology choices. It uses the survey input data for owner-occupiers *hp_survey_oo*. A new initial state is generated for each ABM run (randomisation). This ensures that the results do not depend on a particular set of imputed variables.

```{r initialiser}, paged.print=T}
library(hpmicrosimr)
initialise_agents(sD,2015, cal_run=sample(1:100,1))
```
